Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-06 paper/paper.tex
review introduction

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for
linear control, spanning many areas such as environmental control and
robotic manipulations. The downside to this approach is that in order
to achieve low prices, devices are often limited in their
capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers. In most cases a floating point
implementation is not feasible and the system can benefit from the
added resolution of a fixed point representation. The ubiquity of
these devices requires that they have a robust design that ensures the
correct behaviour in a number of environments.  % For this reason it is
% necessary to provide design tools that formally verify the correctness
% of the digital controller.

\cdsay{Mention that the resulting systems are also expected to have certain properties, 
e.g. stability, which makes it even more difficult to synthesise the controllers?}

In this paper, we explore the automatic synthesis of 
{\em correct-by-construction} controllers, which 
reduces the deveopment cost and design time for a number of models.  
In particular, we are interested in synthesising controllers 
for {\em hybrid closed-loop systems}, i.e., embedded controllers along with a model of their
physical environment, the plant, as shown in
Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
of such systems, we focus on linear models with known configurations
to perform parametric synthesis of the controller dynamics.

>>>>

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for
linear control, spanning many areas such as environmental control and
robotic manipulations \textcolor{red}{Dario: could you please insert a citation here?}. 
The downside to this approach is that in order
to achieve low prices, devices are often limited in their
capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers. In most cases a floating-point
implementation is not feasible and the system can benefit from the
added resolution of a fixed-point representation. The ubiquity of
these devices requires that they have a robust design that ensures the
correct behaviour in a number of different environments.  % For this reason it is
% necessary to provide design tools that formally verify the correctness
% of the digital controller.

There has been previous work to formally verify uncertain linear systems stability 
in digital controllers with considerations to the implementation aspects~\cite{Bessa16}.
In particular, Bessa {\it et al.} considers finite-word length
(FWL) effects over controllers and also parameter uncertainties
in the context of verifying the (so-called) robust non-fragile stability.
However, the authors do not consider the compete range of approximations, 
related to time discretisation, and quantisation effects. Additionally, they do not find 
a parametric solution for a digital controller given a continuous plant specification, 
in order to synthesize the controller implementation.

In this paper, however, we explore the automatic synthesis of 
{\em correct-by-construction} controllers, which 
reduces the deveopment cost and design time for a number of models.  
In particular, we are interested in synthesising controllers 
for {\em hybrid closed-loop systems}, i.e., embedded controllers along with a model of their
physical environment, the plant, as shown in
Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
of such systems, we focus on linear models with known configurations
to perform parametric synthesis of the controller dynamics.
